---
title: "Weight of Fish"
author: "Kimberly Salazar"
date: "`10/31/2024`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(car)
require(leaps)
```

# Predicting Fish Weight
```{r}
fish <- read.csv(file = "Fish.csv")
```

```{r eval=TRUE}
 
fish <- fish %>%
mutate(across(where(is.character), as.factor))
levels(fish$Species)
Bream <- filter(fish, Species == "Bream")
Bream <- select(Bream, -Species) 
Parkki <- filter(fish, Species == "Parkki")
Parkki <- select(Parkki, -Species) 
Perch <- filter(fish, Species == "Perch")
Perch <- select(Perch, -Species) 
Pike <- filter(fish, Species == "Pike")
Pike <- select(Pike, -Species) 
Roach <- filter(fish, Species == "Roach")
Roach <- select(Roach, -Species) 
Smelt <- filter(fish, Species == "Smelt")
Smelt <- select(Smelt, -Species) 
Whitefish <- filter(fish, Species == "Whitefish")
Whitefish <- select(Whitefish, -Species) 
```
Use leap 3 times for each fish

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
require(tidyverse)
if(!require("Bolstad")) {install.packages("Bolstad");require("Bolstad")}

data(bears)
Bears <- select(bears,contains("e"),-Name)
#Clean missing values out of dataset (needed to run Anova at end of demo)
Bears<- na.omit(Bears)
```

# For each of the three species of fish listed below, determine the best regression model and also the best 2 element regression model. Use the BestSubset Regression helper file.


## Perch



```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

This shows the height and weight variables to be the best model. Which also shows to be the best two variables and can be proven using coding.



### Best Models
```{r}
which.max(summary.out$adjr2)
```

### Best Two regressor model
```{r}
summary.out$which[2,]
```
 The best model of the perch fish is model 2, this data summary the best model has the highest adjusted   r-squared value and that model has two variables meaning 2 is the best two regression model.
 
## Pike

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

The best model appears to be the model including all L1, L2, L3, H, and W. While the best two regessor model appears to be the model including L1 and L3.

### Best Models
```{r}
which.max(summary.out$adjr2)
```
The model using all 5 is the best model.

### Best Two regressor model

Using leaps we were able to focus its power onto the adjusted r-squared value. Then it would give us only the highest of adjusted r-squared values for 1, 2, 3, 4 and 5 variables for pike. Using this kind of leaps it shows that L1 and L3 are the best two regreseors for the highest adjusted r-squared value making it the best 2 regressor model.

## Roach
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomleft",main="Adjusted R^2")
```

The best model appears to be the model with 2 variables including L3 and W which means it is also the best two regressor model.

### Best Models
```{r}
which.max(summary.out$adjr2)
```
This shows that the best model is the one with two variables based off the leaps that is targeting the adjusted r-squared value. The two variables in the leaps model is L3 and W.

### Best Two regressor model
Leaps has shown the model with the highest adjusted r-squared value has two variables which are L3and W. So the best 2 regressor model is the one that includes L3 and W. 

## Final Summary Statements